Journal Article Sampling Methodology

### 2016-12-07 src/README.Rmd
Update list sampling methods
Select only articles from the top 10 journals so that only higher level
journals are included

journal_list[1:20, -4] # drop h-index median value
```

@@

```{r journal_sample_order}
journals <- as.data.frame(sample(1:20, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

>>>>

journal_list[1:20, -4] # drop h-index median value just to tidy things up.

journal_list[1:10, ] # select the top ten journals in plant pathology only
```

@@

```{r journal_sample_order}
journals <- as.data.frame(sample(1:10, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```
